Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-06-23 manuscript/manuscript.Rmd
adds stats tests for climate effects reducing skill

Despite the weak climate effects, including climate covariates did increase the accuracy of forecasts for two species: *B. gracilis* and *Poa secunda* (Fig. 2).
Only for *B. gracilis* were the skill increases significant for the IPM ($t_{(279)}$ = 1.70, *P* = 0.045) and the QBM ($t_{(279)}$ = 1.80, *P* = 0.037).
Similarly, forecast error decreased significantly with the inclusion of climate covariates for the *B. gracilis* IPM ($t_{(280)}$ = -3.72, *P* = 0.029) and QBM ($t_{(280)}$ = -3.34, *P* < 0.0001), and for the *Poa secunda* IPM ($t_{(196)}$ = -1.90, *P* < 0.0001) and QBM ($t_{(196)}$ = -2.47, *P* = 0.007) (Fig. S2, Supporting Information).
IPM forecasts were significantly more accurate than the QBM in only one case (Fig. 2): forecast accuracy of *P. smithii* percent cover from an IPM with climate covariates was greater than the accuracy from the QBM with climate covariates ($t_{(215)}$ = 1.92, *P* = 0.028).
However, including climate covariates in the IPM did not significantly increase forecast skill for *P. smithii* (Fig. 2).
Results from all pairwise statistical tests are shown in Table S21 of the Supporting Information.

>>>>

Despite the weak climate effects, including climate covariates did increase the accuracy of forecasts for two species: *B. gracilis* and *Poa secunda* (Fig. 2).
In no case did including climate covariates significantly decrease forecast skill (Table S21), despite small changes in the mean skill (Fig. 2)
Only for *B. gracilis* were the skill increases significant for the IPM ($t_{(279)}$ = 1.70, *P* = 0.045) and the QBM ($t_{(279)}$ = 1.80, *P* = 0.037).
Similarly, forecast error decreased significantly with the inclusion of climate covariates for the *B. gracilis* IPM ($t_{(280)}$ = -3.72, *P* = 0.029) and QBM ($t_{(280)}$ = -3.34, *P* < 0.0001), and for the *Poa secunda* IPM ($t_{(196)}$ = -1.90, *P* < 0.0001) and QBM ($t_{(196)}$ = -2.47, *P* = 0.007) (Fig. S2, Supporting Information).
IPM forecasts were significantly more accurate than the QBM in only one case (Fig. 2): forecast accuracy of *P. smithii* percent cover from an IPM with climate covariates was greater than the accuracy from the QBM with climate covariates ($t_{(215)}$ = 1.92, *P* = 0.028).
However, including climate covariates in the IPM did not significantly increase forecast skill for *P. smithii* (Fig. 2).
Results from all pairwise statistical tests are shown in Table S22 of the Supporting Information.
